% !TEX program = xelatex

\documentclass{resume}
 
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Brett Sandler}

% {E-mail}{mobilephone}{homepage}{address}
\contactInfo{sandler.brett@gmail.com}{+1 (248) 508-7336}
            {www.github.com/sandlerb}
            {1602 Packard, Apt. B4, Ann Arbor, MI 48104}
 
\section{\faWrench\ Experience}
\jobheader{\textbf{Stratos Technologies}}{Embedded Engineer}
          {May 2014 -- Present}
My responsibilities include firmware development, manufacturing
root causing, and test system development for a Bluetooth-enabled payment
platform.  As a cross-functional embedded engineer I am involved in managing
manufacturing engineering efforts, quality assurance, and product development.
\begin{itemize}
  \item Developed and maintained ultra low power firmware on a PIC18. This
      included a minimal bootloader supporting over-the-air application
      upgrades as well as the primary application
  \item Performed power analysis and accelerated life testing to evaluate the
      usable lifetime of the Stratos card
  \item Re-engineered the software used in manufacturing test. This 
      significantly increased visibility and confidence throughout the 
      electronics manufacturing process
  \item Supported global manufacturing partners remotely and on the factory floor
\end{itemize}
\vspace{3mm}

\jobheader{\textbf{Quantum Signal}}{Engineering Intern}{May 2013 -- Dec. 2013}
Contributed to various projects ranging from an in-house reflow oven to robotics
simulation software.
\begin{itemize}
  \item Designed and programmed circuit boards for control systems
  \item Wrote control software for lidar and time-of-flight cameras
  \item Implemented new features in a robotics simulation application
\end{itemize}
\vspace{3mm}

\jobheader{\textbf{Intergalactic Mobile Learning Center}}{Research Assistant}
          {May 2012 -- May 2013}
Developed the Personal Instrumentation Environment, an Android-based sensor
kit intended for use in K-12 classrooms.
\begin{itemize}
  \item Designed a microcontroller-based front end for a modular set of sensors
  \item Wrote firmware and an Android application to log data from the hardware
      front end
\end{itemize}
\vspace{3mm}

\jobheader{\textbf{Kurdak Research Group}}{Research Assistant}
          {Sep. 2011 -- Sep. 2012}
Çagliyan Kurdak's research concerns the subfield of mesoscopic physics. As a
member of his group I was exposed to low temperature semiconductor research and
provided the technical support to automate experiments.
\begin{itemize}
  \item Programmed the control board and PC front end for a system to analyze the
      properties of an experimental lithium-ion battery network
  \item Measured and analyzed rechargeable lithium-ion battery candidates for the
      proposed network
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Michigan}, Ann Arbor}{Graduated 2013}
\textit{B.S.} in Physics
\newline
\textit{Minor} in Computer Science

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C, Python, C++, Java
  \item Platforms: Linux, Windows, Mac OS X, PIC, 8051, ARM
\end{itemize}

\end{document}
